---
title: "S2 - NPIs"
output: 
  html_document:
    toc: true
    toc_float:
      smooth_scroll: FALSE
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(dplyr)
library(gt)
library(kableExtra)
library(Metrics)
library(pomp)
library(purrr)
library(readr)
library(readsdr)
library(stringr)
library(tictoc)
library(tidyr)

source("./R_scripts/plots.R")
source("./R_scripts/R0_estimation.R")
source("./R_scripts/optim_est.R")

pop_val   <- 17475415
beta_vals <- 0.724637681 * c(1, 1.5, 2)
zeta_val  <- beta_vals[[2]] * 10

bio_df <- read_csv("./Data/bio_params.csv", 
                       show_col_types = FALSE)

bio_params        <- as.list(bio_df$Value)
names(bio_params) <- bio_df$Parameter

delta_val <- 0.6
```

This electronic supplementary material supports the results presented in the 
main text regarding the sub-models representing the non-pharmaceutical 
interventions  (**NPIs**). Specifically, this HTML file is the rendered version 
of a dynamic document (R markdown) containing the *R* code that simulates the 
models and produces the plots shown in the main text. Additionally, this file
includes supplementary information to complement the discussion in the main 
text.


# Testing & Isolation (*T&I*)

## Equations

Compared to the SEI3R model (*1A_SEI3R.stmx*), T&I models 
(*2A_TI_fixed_fractions.stmx* & *2B_TI_Logistic.stmx*) modify the dynamics
of transmission in the following way:

\begin{equation} \label{eq:1}
  \begin{aligned}
    \dot{P^d_t}   &= \theta_t \omega \sigma E_t - \nu P^d_t\\
    \dot{P_t}     &= (1- \theta_t) \omega \sigma E_t - \nu P_t\\
    \dot{I^d_t}   &= \nu P^d_t - \gamma I^d_t\\
    \dot{R_t}   &= \gamma (I_t + I^d_t) + \kappa A_t \\
    \lambda_t   &= \frac{\beta (P_t +  I_t + P^d_t + (1 -\iota^d) I^d_t + \eta A_t)}{N}
    \end{aligned}
\end{equation}

## Comparison

### Fixed testing fraction

First, we simulate the *T&I* with a constant testing fraction
($\theta^d$) under three scenarios, where $\theta$ takes the following
values: *0%*, *25%*, *50%*. 

```{r}
# Model with a constant intervention
c_mdl <- read_xmile("./models/2A_TI_fixed_fractions.stmx", 
                    const_list = c(bio_params))

theta_df <- data.frame(par_theta_d = c(0, 0.25, 0.5))

f_t_sens_df <- sd_sensitivity_run(c_mdl$deSolve_components, 
                              consts_df = theta_df,
                              integ_method = "euler", start_time = 0,
                              stop_time = 1000, timestep = 1 / 64,
                              multicore = TRUE, n_cores = 3,
                              reporting_interval = 1 / 8) |> 
  mutate(c = C / N)
```


```{r}
# Fixed testing
f_t_df <- f_t_sens_df |> 
  filter(time > 0 & time <= 150) |> 
  select(time, c, E_to_Pd, par_theta_d) |> 
  mutate(E_to_Pd = 1000 * E_to_Pd / pop_val,
         c = c * 100,
         var_theta = par_theta_d * 100) |> 
  pivot_longer(c(-time, -par_theta_d)) |> 
  mutate(par_theta_d = percent(par_theta_d),
         name = case_when(name == "c" ~ "Attack rate [%]",
                          name == "E_to_Pd" ~ "Daily tests per 1000 population",
                          name == "var_theta" ~"Testing fraction [%]")) 
```

### Time-varying testing fraction

We model the time-varying testing fraction using the logistic growth model. To 
configure this structure, we employ data^[https://archief51.sitearchief.nl/archives/sitearchief/20230629020000/https://www.diensttesten.nl/over-dienst-testen/historie-van-dienst-testen] from the COVID-19 pandemic in the Netherlands (see below) and 
model calibration to estimate the logistic growth model's parameters. 

- In March 2020 the reported test capacity in the Netherlands was 4000 tests per 
day. 

- In June 2020 the Netherlands was able to conduct 30.000 tests per day.

- By the end of 2020 the capacity has grown to 120.000 tests per day.

- In April 2021 the capacity had grown to 175.000 test per day.

```{r}
data_df <- data.frame(time  = c(0, 90, 300, 390),
                      value = c(4000, 30000, 120000, 175000)) |>
  mutate(value = value * 1000 / pop_val)

est_obj <- estimate_rho(data_df)
rho_est <- est_obj$estimate 

# Testing capacity parameters
tc_pars <- data.frame(name  = c("alpha_d", "rho_d", "Qd"),
                      value = c(data_df[4, 2], rho_est, data_df[1, 2])) |> 
  write_csv("./Data/Testing_capacity_pars.csv")
```

```{r, fig.cap = "Fig 1. Testing capacity"}
plot_fit(est_obj$sim, data_df)
```

Using the capacity estimates, we simulate the *testing and isolation* model.

```{r}
fp <- "./models/2B_TI_Logistic.stmx"

iota_mid <- 0.51

alpha_d_val <- data_df[4, 2]
Qd_init     <- data_df[1, 2]

mdl       <- read_xmile(fp, 
                        stock_list = list(Qd = Qd_init),
                        const_list = c(bio_params,
                                       par_beta    = beta_vals[[2]],
                                       par_alpha_d = alpha_d_val,
                                       par_rho_d   = rho_est,
                                       par_iota_d  = 0.51,
                                       par_delta   = 0.60))
ds_inputs <- mdl$deSolve_components

output <- sd_simulate(ds_inputs, start_time = 0, stop_time = 1000, 
                      timestep = 1 / 64,
                      integ_method = "euler") |> 
  mutate(c     = C / pop_val)
```

```{r}
# This data frame summarises key indicators from the previous simulation
tv_df <- output |> select(time, c, E_to_Pd, Qd, var_theta) |> 
  mutate(E_to_Pd = 1000 * E_to_Pd / pop_val,
         c = c * 100,
         var_theta = var_theta * 100) |> 
  filter(time > 0 & time <= 150) |> 
  pivot_longer(-time) |> 
  mutate(name = case_when(name == "c" ~ "Attack rate [%]",
                          name == "E_to_Pd" ~ "Daily tests per 1000 population",
                          name == "Qd" ~ "Testing capacity per 1000 population",
                          name == "var_theta" ~"Testing fraction [%]")) 
```

This table compares the attack rate at day 150 between the two assumptions
(fixed and time-varying testing rates).

```{r}
tv_attack_rate <- output |> filter(time == 150) |>
  mutate(par_theta_d = "Time-varying",
         c         = percent(round(c, 2))) |>
  select(par_theta_d, C, c)

f_t_sens_df |> filter(time == 150) |> select(par_theta_d, C, c) |>
  mutate(par_theta_d = percent(par_theta_d),
         c         = percent(round(c, 2))) |>
  bind_rows(tv_attack_rate) |>
  gt() |>
    cols_label(
    par_theta_d = html("Testing fraction (&theta;<sup>d</sup>)"),
    c = html("Attack rate by day 150 (c<sub>150</sub>)"),
    C = html("Cumulative infections by day 150 (C<sub>150</sub>)")) |>
    tab_style(
      style = list(
      cell_text(color = "#0363BB")),
    locations = cells_body(
      rows = 4))
```

# Testing, tracing and Isolation (*TTI*)

TTI refers to the combined strategy of testing and isolation plus contact 
tracing.

## Equations

Compared to the T&I models (*2A_TI_fixed_fractions.stmx* & 
*2B_TI_Logistic.stmx*), the TTI structure (*2C_TTI_Logistic.stmx* & 
*2D_TTI_fixed_fractions.stmx*) modify the dynamics of transmission in the following way:


\begin{equation} \label{eq:2}
  \begin{aligned}
    \dot{S_t}       &= -\lambda_t S_t + \frac{S^q_t}{\sigma^-{1} + \nu^{-1} +
      \gamma^{-1}} - \mu^s_t S_t - \mu^i_t S_t \\
    \dot{S^q_t}     &= \mu^s_t S_t - \frac{S^q_t}{\sigma^-{1} + \nu^{-1} +\gamma^{-1}}\\
    \dot{E^q_t}     &= \mu^i_t S_t - \sigma E^q_t\\
    \dot{P^q_t}     &= \omega \sigma E^q_t - \nu P^q_t\\
    \dot{I^q_t}     &= \nu P^q_t - \gamma I^q_t\\
    \dot{A^q_t}     &= (1 - \omega) \sigma E^q_t - \kappa A^q_t\\
    \dot{R_t}       &= \gamma (I_t + I^d_t + I^q_t) + \kappa (A_t + A^q_t) \\
    \lambda_t       &= \lambda^{P}_t + \lambda^{P^d}_t + \lambda^{P^q}_t +
      \lambda^{I}_t + \lambda^{I^d}_t + \lambda^{I^q}_t + \lambda^{A}_t +
      \lambda^{A^q}_t\\
    \lambda^{P^q}_t &= (1 - \iota^d) \frac{\beta P^q_t} {N}\\
    \lambda^{I^q}_t &= (1 - \iota^d) \frac{\beta I^q_t} {N} \\
    \lambda^{A^q}_t &= (1 - \iota^d) \frac{\eta \beta A^q_t}{N} \\
    \lambda^{P^d}_t &= \frac{\upsilon (\zeta - \zeta^k_t) P^d_t}{N} \\
    D^k_t           &= \zeta P^d_t\\
    k_t             &= \min(D^k_t , Q^k_t) \\
    \zeta^k_t       &= \begin{cases}
    0,   P^d = 0 \\
    \frac{k_t}{P^d}, P^d > 0
    \end{cases}\\
    \mu^s_t         &= \frac{(1 - \upsilon) \zeta^k_t P_t^d}{N}\\
    \mu^i_t         &=  \frac{\upsilon \zeta^k_t P_t^d}{N}
  \end{aligned}
\end{equation}

## $\Re_0$ analytical expression

We employ the Next Generation Matrix method to derive an analytical expression
for the basic reproduction number. See file *./Mathematica_notebooks/TTI_RO.nb* 
in the Github [repository](https://github.com/jandraor/preparedness).

### F matrix

```{r, message = FALSE}
F_matrix           <- read_csv("./Data/CT_F_matrix.csv", show_col_types = FALSE)
c_names            <- colnames(F_matrix)
c_names[1]         <- ""
colnames(F_matrix) <- c_names

F_matrix |>
  kbl(escape = FALSE) |> kable_styling(full_width = FALSE)
```

### V matrix

```{r, message = FALSE}
F_matrix           <- read_csv("./Data/CT_V_matrix.csv", show_col_types = FALSE)
c_names            <- colnames(F_matrix)
c_names[1]         <- ""
colnames(F_matrix) <- c_names

F_matrix |>
  kbl(escape = FALSE) |> kable_styling(full_width = FALSE)
```

### Spectral radius (largest eigenvalue)

\begin{equation}

a = \sqrt{\gamma ^4 \kappa ^2 \upsilon ^2 \left((\gamma  (\zeta  \eta  \nu  (\omega -1)-\zeta  \kappa  \omega + \zeta^k \theta  \kappa  \omega )+\zeta  \kappa  \nu  \omega  (\theta  \iota^d -1))^2-4 \gamma  \zeta  \zeta^k \theta  (\iota^d -1) \kappa  \omega  (\gamma  \eta  (\nu -\nu  \omega )+\gamma  \kappa  \omega +\kappa  \nu  \omega )\right)}

\end{equation}

\begin{equation}

b = \gamma ^3 \kappa  \upsilon  (\zeta  \eta  (\nu -\nu  \omega )+\zeta  \kappa  \omega - \zeta^k \theta  \kappa  \omega )+\gamma ^2 \zeta  \kappa ^2 \nu  \upsilon  \omega  (1-\theta  \iota^d )

\end{equation}

\begin{equation}

\Re_0 = \frac{a + b}{2 \gamma ^3 \kappa ^2 \nu}

\end{equation}

## Comparison

### Fixed testing & tracing fractions

We simulate the *TTI* model with constant testing ($\theta^d$) and tracing
($\theta^k$) fractions underthree scenarios. These fractions can take the
following values: *0%*, *25%*, *50%*.

```{r}
# Testing, tracing, and isolation with fixed testing and tracing fractions
f_ct_path <- "./models/2D_TTI_fixed_fractions.stmx"

f_ct_mdl <- read_xmile(f_ct_path, 
                       const_list = c(bio_params,
                                      par_zeta = zeta_val))

theta_df <- data.frame(par_theta_d = c(0, 0.25, 0.5),
                       par_theta_k = c(0, 0.25, 0.5))

c_sens_df <- sd_sensitivity_run(f_ct_mdl$deSolve_components, 
                              consts_df = theta_df,
                              integ_method = "euler", start_time = 0,
                              stop_time = 1000, timestep = 1 / 64,
                              multicore = TRUE, n_cores = 3,
                              reporting_interval = 1 / 8) |> 
  mutate(c = C / N)
```


```{r}
# Fixed testing & tracing
f_ct_df <- c_sens_df |> 
  filter(time > 0 & time <= 150) |> 
  select(time, c, k, par_theta_k) |> 
  mutate(c = c * 100,
         tracing_rate     = 1000 * k / pop_val,
         var_theta_k = par_theta_k * 100) |> 
  select(-k) |> 
  pivot_longer(c(-time, -par_theta_k)) |> 
  mutate(par_theta_k = percent(par_theta_k),
         name = case_when(name == "c" ~ "Attack rate [%]",
                          name == "tracing_rate" ~ "Daily tracings per 1000 population",
                          name == "var_theta_k" ~"Tracing fraction [%]")) 
```

### Time-varying testing fraction

We model the time-varying tracing fraction using the logistic growth model. To 
configure this structure, we employ data^[https://ggdghor.nl/actueel-bericht/werving-bron-en-contactonderzoek/] 
from the COVID-19 pandemic in the Netherlands (see below) and 
model calibration to estimate the logistic growth model's parameters. 

At the start of the pandemic tracing capacity was around 200-220 FTE. By May 
2020, this value tripled to 670 FTE. From June 2020, the capacity of the GGD 
was significantly expanded to a total of 1250 FTE. By the end of September 2020,
this capacity was expected to reach 3250 FTE. 


```{r}
data_FTE <- data.frame(time  = c(0, 60, 90, 210),
                      value = c(200, 670, 1250, 3250)) 

est_obj     <- estimate_rho(data_FTE)
rho_k_est   <- est_obj$estimate
```


```{r, fig.cap = "Fig 2. Tracing capacity"}
plot_fit(est_obj$sim, data_FTE)
```

Using the capacity estimates, we simulate the *TTI* model.

```{r}
fp_ct <- "./models/2C_TTI_Logistic.stmx"

zeta_val   <- beta_vals[[2]] * 10

# Number of index cases traced per week per FTE
idx_val <- 3

Qk_init     <- (data_FTE[1, 2] * idx_val * zeta_val / 7) * (1000 / pop_val)
alpha_k_val <- (data_FTE[4, 2] * idx_val * zeta_val / 7) * (1000 / pop_val)

iota_mid <- 0.51

alpha_d_val <- data_df[4, 2]

ct_pars <- data.frame(name  = c("alpha_k", "rho_k", "Qk"), 
                      value = c(alpha_k_val, rho_k_est, Qk_init)) |> 
  write_csv("./Data/Tracing_capacity_pars.csv")

mdl       <- read_xmile(fp_ct, stock_list = list(Qd = data_df[1, 2],
                                              Qk = Qk_init),
                        const_list = c(bio_params,
                                       par_zeta    = zeta_val,
                                       par_alpha_d = alpha_d_val,
                                       par_alpha_k = alpha_k_val,
                                       par_rho_d   = rho_est,
                                       par_rho_k   = rho_k_est,
                                       par_iota_d  = 0.51,
                                       par_delta   = 0.60))
ds_inputs <- mdl$deSolve_components

sim_output <- sd_simulate(ds_inputs, start_time = 0, stop_time = 300, 
                          timestep = 1 / 64, integ_method = "euler") |> 
  mutate(c = C / N)
```

Then, we calculate the effective reproduction number...

```{r}
Re_df <- sim_output |> 
  mutate(R_number = estimate_R0_tti(par_zeta = par_zeta,
                                   par_upsilon = par_upsilon,
                                   var_theta = var_theta,
                                   par_iota = par_iota_d,
                                   var_zeta_k = var_zeta_k,
                                   bio_params = bio_params),
         s = S / N,
         Rt = R_number * s) |> 
  select(time, Rt)
```

and indicators over time.

```{r}
# Time-varying (tv) contact tracing (ct)
tv_ct_df <- sim_output  |> select(time, c, k, Qk, Dk) |> 
  mutate(c                = c * 100,
         tracing_rate     = 1000 * k / pop_val,
         tracing_fraction = k/Dk * 100) |> 
  filter(time > 0 & time <= 150) |> 
  select(-k, -Dk) |> 
  pivot_longer(-time) |> 
  mutate(name = case_when(name == "c" ~ "Attack rate [%]",
                          name == "tracing_rate" ~ "Daily tracings per 1000 population",
                          name == "Qk" ~ "Tracing capacity per 1000 population",
                          name == "tracing_fraction" ~"Tracing fraction [%]")) 
```

This table compares the attack rate at day 150 between the two assumptions
(fixed and time-varying testing rates).

```{r}
# Indicators from the scenario with time-varying fractions at day 150

tv_ind_150 <- sim_output |> filter(time == 150) |>
  mutate(par_theta_k = "Time-varying",
         c         = percent(round(c, 2))) |>
  select(par_theta_k, c, C)

c_sens_df |> filter(time == 150) |> select(par_theta_k, c, C) |>
  mutate(par_theta_k = percent(par_theta_k),
         c         = percent(round(c, 2))) |>
  bind_rows(tv_ind_150) |>
  gt() |>
    cols_label(
    par_theta_k = html("Testing & tracing fraction (&theta;)"),
    c = html("Attack rate at day 150 (c<sub>150</sub>)"),
    C = html("Cumulative infections by day 150 (C<sub>150</sub>)")) |>
    tab_style(
      style = list(
      cell_text(color = "#0363BB")),
    locations = cells_body(
      rows = 4))
```

This code produces Fig 4 in the main text.

```{r, fig.height = 7.5}
g <- plot_fig_04(tv_df, f_t_df, tv_ct_df, f_ct_df, Re_df)

ggsave("./plots/Fig_04_TI_CT.pdf", plot = g, 
       height = 7, width = 7, device = cairo_pdf)
```

## Testing and tracing scenarios

```{r}
ref_testing <- tc_pars |> pivot_wider() |> 
  rename(par_alpha_d = alpha_d,
         par_rho_d = rho_d)

test_sc_1 <- ref_testing |> mutate(par_rho_d = par_rho_d * 2,
                                   Testing_scenario = "t1")

test_sc_2 <- ref_testing |> mutate(par_rho_d = 0,
                                   Qd = par_alpha_d,
                                   Testing_scenario = "t2")

test_sc_3 <- ref_testing |> mutate(par_rho_d = 0,
                                   par_alpha_d = par_alpha_d * 2,
                                   Qd = par_alpha_d,
                                   Testing_scenario = "t3")

test_sc <- bind_rows(test_sc_1, test_sc_2, test_sc_3)
```

```{r}
ref_tracing <- ct_pars |> pivot_wider() |> 
  rename(par_alpha_k = alpha_k,
         par_rho_k = rho_k)

trac_sc_1 <- ref_tracing  |> mutate(par_rho_k = par_rho_k * 2,
                                   Tracing_scenario = "c1")

trac_sc_2 <- ref_tracing  |> mutate(par_rho_k = 0,
                                    Qk = par_alpha_k,
                                    Tracing_scenario = "c2")

trac_sc_3 <- ref_tracing  |> mutate(par_rho_k   = 0,
                                    par_alpha_k = par_alpha_k * 2,
                                    Qk          = par_alpha_k,
                                   Tracing_scenario = "c3")

trac_sc <- bind_rows(trac_sc_1, trac_sc_2, trac_sc_3)
```

```{r}
scenarios_df <- expand.grid(Testing_scenario = paste0("t", 1:3), 
            Tracing_scenario = paste0("c", 1:3)) |> 
  left_join(test_sc) |> 
  left_join(trac_sc) |> 
  mutate(iter = row_number())
```

```{r}
scenarios_df |>
  select(-iter) |> 
  mutate(across(where(is.numeric),~round(.x, 2))) |> 
  gt() |>
    cols_label(
    par_alpha_d      = html("&alpha;<sup>d</sup>"),
    par_rho_d        = html("&rho;<sup>d</sup>"),
    Qd               = html("Q<sub>0</sub><sup>d</sup>"),
    par_alpha_k      = html("&alpha;<sup>k</sup>"),
    par_rho_k        = html("&rho;<sup>k</sup>"),
    Qk               = html("Q<sub>0</sub><sup>k</sup>"),
    Testing_scenario = "Testing scenario",
    Tracing_scenario = "Tracing scenario")
```

```{r}
fp_ct <- "./models/2C_TTI_Logistic.stmx"

zeta_val  <- beta_vals[[2]] * 10
iota_mid  <- 0.51
delta_mid <- 0.6

mdl <- read_xmile(fp_ct,
                  const_list = c(bio_params,
                                 par_iota_d  = iota_mid,
                                 par_delta   = delta_mid))

sim_sce_df <- sd_sensitivity_run(mdl$deSolve_components, 
                             consts_df = scenarios_df[,
                                                      c("par_alpha_d", "par_rho_d", 
                                                        "par_alpha_k", "par_rho_k")],
                             stocks_df = scenarios_df[, c("Qd", "Qk")],
                             integ_method = "euler", start_time = 0,
                             stop_time = 1000, timestep = 1 / 64,
                             multicore = TRUE, n_cores = 3,
                             reporting_interval = 1 / 8)
```

```{r}
sim_sce_df |> filter(time == 150) |> 
  mutate(c = percent(round(C / pop_val, 2))) |> 
  left_join(scenarios_df[, c("iter", "Testing_scenario", "Tracing_scenario")]) |> 
  select(Testing_scenario, Tracing_scenario, c) |>
  arrange(Testing_scenario) |> 
  gt() |> 
    cols_label(
    Testing_scenario = "Testing scenario",
    Tracing_scenario = "Tracing scenario",
    c = html("Attack rate at day 150 (c<sub>150</sub>)"))
```

```{r}
cap_df <- sim_sce_df |> select(time, Qd, Qk, iter) |> 
  filter(time <= 120,
         iter %in% c(1, 5, 9)) |> 
  left_join(scenarios_df[, c("iter", "Testing_scenario", "Tracing_scenario")])
```


```{r}
inc_df <- sim_sce_df |> select(iter, time, C_in) |> 
  filter(time <= 120) |> 
  left_join(scenarios_df[, c("iter", "Testing_scenario", "Tracing_scenario")])
```

This code produces Fig 6 in the main text.

```{r}
g <- plot_fig_06(cap_df, inc_df, sim_output)

ggsave("./plots/Fig_06_TI_CT_Scenarios.pdf", plot = g, 
       height = 7, width = 7, device = cairo_pdf)
```

## Compliance scenarios

We simulate the TTI model under three scenarios of individual compliance.

```{r}
iota_high  <- 0.62
delta_high <- 0.9
comp_scn <- data.frame(par_iota_d = c(iota_mid, iota_high, iota_high),
                       par_delta  = c(delta_high, delta_val, delta_high)) 

fp_ct <- "./models/2C_TTI_Logistic.stmx"

mdl <- read_xmile(fp_ct,
                  list(Qd = data_df[1, 2],
                       Qk = Qk_init),
                  const_list = c(bio_params,
                                 par_zeta = zeta_val,
                                 par_alpha_d = alpha_d_val,
                                 par_alpha_k = alpha_k_val,
                                 par_rho_d   = rho_est,
                                 par_rho_k   = rho_k_est))

comp_sce_df <- sd_sensitivity_run(mdl$deSolve_components, 
                                  consts_df = comp_scn,
                                  integ_method = "euler", start_time = 0,
                                  stop_time = 1000, timestep = 1 / 64,
                                  reporting_interval = 1 / 8)
```

## Detecting pre-clinical individuals

We simulate a variant of TTI model, where the detection of infectious 
individuals occurs at the pre-clinical (pre-symptomatic) stage.

```{r}
comp_scn2 <- bind_rows(data.frame(par_iota_d = iota_mid,
                                  par_delta  = delta_val), comp_scn) 

mdl_4d_fp <- "./models/2E_TTI_logistic_pre_symp.stmx"

mdl_4d <- read_xmile(mdl_4d_fp,
                     list(Qd = data_df[1, 2],
                          Qk = Qk_init),
                     const_list = c(bio_params,
                     par_zeta = zeta_val,
                     par_alpha_d = alpha_d_val,
                     par_alpha_k = alpha_k_val,
                     par_rho_d   = rho_est,
                     par_rho_k   = rho_k_est))

mdl_4d_sce_df <- sd_sensitivity_run(mdl_4d$deSolve_components, 
                                    consts_df = comp_scn2,
                                    integ_method = "euler", start_time = 0,
                                    stop_time = 500, timestep = 1 / 64,
                                    reporting_interval = 1 / 8)
```

This code produces Fig 7 in the main text.

```{r, fig.height = 7}
g <- plot_fig_07(comp_sce_df, mdl_4d_sce_df, sim_output, comp_scn, inc_df)

ggsave("./plots/Fig_07_CT_sensitivity.pdf", plot = g, 
       height = 6, width = 7, device = cairo_pdf)
```


# TTI + mobility restrictions (MR)

```{r}
mdl_ct_mob_fp <- "./models/2F_TTI_PLUS_MR.stmx"

mdl_ct_mob <- read_xmile(mdl_ct_mob_fp,
                         const_list  = c(bio_params,
                                         par_zeta_0  = zeta_val,
                                         par_alpha_d = alpha_d_val,
                                         par_alpha_k = alpha_k_val,
                                         par_rho_d   = rho_est,
                                         par_rho_k   = rho_k_est,
                                         par_iota_d  = iota_mid,
                                         par_delta   = delta_mid),
                         stock_list = c(Qd = Qd_init,
                                        Qk = Qk_init,
                                        Qm = 90))
```

This code simulates the model that incorporates testing, tracing, and isolation
(TTI) and mobility restrictions (MR). In other words, the three 
non-pharmaceutical interventions explored in this work. This simulation explores
three scenarios: 

1. Mobility restrictions without TTI
2. TTI + mobility restrictions, where the latter are deployed at day 0
2. TTI + mobility restrictions, where the latter are deployed at day 40

```{r}
# First scenario: Just MR
# Second scenario: TTI + MR, starting at 0
# Third scenario: TTI + MR, starting at 40 & optimised stringency

intv_df <- data.frame(par_xi = c(0.8, 0.8, 0.62),
                      par_tau_m = c(0, 0, 40),
                      Qd = c(0, Qd_init, Qd_init),
                      Qm = c(90, 90, 90),
                      itv = c("MR", "TTI + MR", "TTI + MR"),
                      iter = 1:3)

sim_mob_df <- sd_sensitivity_run(mdl_ct_mob$deSolve_components,
                                 consts_df = select(intv_df, par_tau_m, par_xi),
                                 stocks_df = select(intv_df, Qd, Qm),
                                 start_time = 0,
                                 stop_time = 360, 
                                 timestep = 1 / 64, integ_method = "euler",
                               multicore = TRUE, n_cores = 3) |> 
  mutate(c = C / N) |> 
  left_join(intv_df[, c("iter", "itv")])
```

## Sensitivity analysis

This code performs a sensitivity analysis on the *TTI + MR* model. In 
particular, we draw 10 000 points  from a two-dimensional uniform space defined
by the stringency parameter ($\xi$) and the time at which mobility restrictions
are introduced ($\tau^m$). We subsequently use these points to configure and
simulate the *TTI + MR* model. For each simulation, we estimate the
attack rate at days 180 & 270.

```{r}
set.seed(19860618)

grid_df <- expand.grid(par_xi    = seq(from = 0, to = 1, length.out = 100),
                       par_tau_m = seq(from = 0, to = 60, length.out = 100))
```

```{r, fig.cap = "Fig 3. Samples"}
plot(grid_df, pch = 16, cex = 0.5, col = "steelblue",
     xlab = expression(xi), ylab = expression(tau^m))
```

```{r}
fp <- "./saved_objects/mob_ct_sens.rds"

if(!file.exists(fp)) {
  
  sim_mr_scn <- sd_sensitivity_run(mdl_ct_mob$deSolve_components, 
                              consts_df = grid_df,
                              start_time = 0, 
                              stop_time = 365, timestep = 1/64,
                              integ_method = "euler",
                              multicore = TRUE,
                              reporting_interval = 1) |> 
    select(iter, time, C, C_in, par_xi, par_tau_m)
  
  
  saveRDS(sim_mr_scn, fp)
} else {
  sim_mr_scn <- readRDS(fp)
}
```

This code produces Fig 8 in the main text.

```{r, fig.height = 7}
g <- plot_fig_08(sim_mob_df, sim_output, sim_mr_scn)

ggsave("./plots/Fig_08_Mobility.pdf", plot = g, 
       height = 7.5, width = 7, device = cairo_pdf)
```

## The narrow band

Theoretically, the rate of new cases begins its decline when the effective 
reproduction number reaches 1 ($\Re_t = 1$). This change in dynamics happens
when the proportion of susceptible individuals ($s$) falls below the herd
immunity threshold ($\frac{1}{\Re_0}$). If a population could be allowed to
develop immunity naturally until this threshold is reached, followed by strict 
mobility restrictions to drive cases near zero, then lifting those restrictions
would not trigger a re-emergence. In the context of the no-intervention scenario
with $\Re_0 =3$, the target for the susceptible fraction is $\frac{1}{3}$, which
implies that at most *33%* of the population should remain susceptible or that 
at least *67%* should be infected. However, as we saw previously, *TTI* reduces
$\Re_0$ to *2.25* before saturation, implying a new target susceptible fraction 
of $\frac{1}{2.25}$, approximately *44%*.

To corroborate this insight about the target susceptible fraction changing with
*TTI*, we simulate three scenarios (as shown in the figure below). The first 
scenario (blue lines) corresponds to the case where only *TTI* is employed. As 
we have seen previously, the susceptible fraction collapses simply because the
infection runs its course as though there were no interventions. The second 
scenario (beige lines) involves the implementation of *TTI + MR*, where mobility
restrictions are deployed at day 40 with a stringency of 0.8. Although this
intervention reduces $\Re_t$ below the epidemiological threshold (dashed line),
the susceptible fraction remains above the target (dotted line). Therefore, once
the mobility restrictions are lifted, $\Re_t$ rises above the epidemic 
threshold, leading to a second wave of infections. In contrast, the ideal 
scenario (*3*) with a stringency of 0.62 also drives $\Re_t$ below 1 but allows 
the susceptible fraction to reach the intended target. Consequently, when 
mobility restrictions are lifted, $\Re_t$ cannot surge to produce a new 
outbreak.

```{r}
mob_scn <- data.frame(par_xi = c(0, 0.8, 0.62),
                       par_tau_m = 40) |> 
  mutate(Scenario = row_number(), .before = everything())

gt(mob_scn) |> 
  cols_label(
    par_xi    = html("Stringency (&xi;)"),
    par_tau_m = html("Start of intervention (&tau;<sup>m</sup>)")
  )
```


```{r}
# Sensitivity of stringency
sim_str_df <- sd_sensitivity_run(mdl_ct_mob$deSolve_components,
                                 consts_df = select(mob_scn, par_xi, par_tau_m),
                                 start_time = 0,
                                 stop_time = 365, 
                                 timestep = 1 / 64, integ_method = "euler",
                                 multicore = TRUE, n_cores = 3)
```

```{r, fig.cap = "Fig 4. Effect of stringency on disease dynamics"}
sim_str_df <- sim_str_df |> 
  mutate(R_number = estimate_R0_tti(par_zeta = var_zeta_t,
                                   par_upsilon = par_upsilon,
                                   var_theta = var_theta,
                                   par_iota = par_iota_d,
                                   var_zeta_k = var_zeta_k,
                                   bio_params = bio_params),
         s = S / N,
         Rt = R_number * s) |> 
  filter(time > 0)

plot_stringency_comparison(sim_str_df)
```



