---
title: "S2"
output: 
  html_document:
    toc: true
    toc_float:
      smooth_scroll: FALSE
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(kableExtra)
library(Metrics)
library(pomp)
library(purrr)
library(readr)
library(readsdr)
library(stringr)
library(tictoc)
library(tidyr)

source("./R_scripts/plots.R")
source("./R_scripts/R0_estimation.R")
source("./R_scripts/optim_est.R")

pop_val   <- 17475415
beta_vals <- 0.724637681 * c(1, 1.5, 2)
```

```{r}
bio_df <- read_csv("./Data/bio_params.csv", 
                       show_col_types = FALSE)

bio_params        <- as.list(bio_df$Value)
names(bio_params) <- bio_df$Parameter
```

# Base case

```{r}
mdl <- read_xmile("./models/01_SEI3R.stmx", const_list = bio_params)

par_beta_df <- data.frame(par_beta = beta_vals)

sens_df <- sd_sensitivity_run(mdl$deSolve_components, 
                              consts_df = par_beta_df,
                              integ_method = "euler", start_time = 0,
                              stop_time = 1000, timestep = 1 / 64,
                              multicore = TRUE, n_cores = 3,
                              reporting_interval = 1 / 8) |> 
  mutate(c      = C / N,
         c_base = c,
         s      = S / N)
```

```{r}
base_df <- sens_df |> select(time, c_base, par_beta, s, C_in) |> 
  mutate(R0 = round(estimate_R0(par_beta, bio_params), 1),
         Rt = R0 * s)

ref_time <- base_df |> filter(R0 == 3) |> 
  mutate(diff_rt = 1 - Rt) |> 
  filter(diff_rt > 0) |> 
  filter(diff_rt == min(diff_rt)) |> 
  pull(time)

ref_peak <- base_df |> filter(R0 == 3) |> 
  filter(C_in == max(C_in)) |> pull(C_in)
```

# Testing & Isolation

```{r}
delta_vals <- c(0.3, 0.6, 0.9)
str_time   <- 0
stp_time   <- 300
```

## Partial calibration

```{r}
data_df <- data.frame(time  = c(0, 90, 300, 390),
                      value = c(4000, 30000, 120000, 175000)) |>
  mutate(value = value * 1000 / pop_val)

est_obj <- estimate_rho(data_df)
rho_est <- est_obj$estimate 
```


```{r}
ggplot(est_obj$sim, aes(time, Q)) +
  geom_line() +
  geom_point(data = data_df, aes(y = value), colour = "red") +
  theme_classic()
```


```{r}
fp <- "./models/03_Testing_Isolation.stmx"

iota_mid <- 0.51

alpha_d_val <- data_df[4, 2]

mdl       <- read_xmile(fp, stock_list = list(Qd = data_df[1, 2]),
                        const_list = c(bio_params,
                                       par_beta    = beta_vals[[2]],
                                       par_alpha_d = alpha_d_val,
                                       par_rho_d   = rho_est,
                                       par_iota_d  = 0.51,
                                       par_delta   = 0.60))
ds_inputs <- mdl$deSolve_components
```

```{r}
output <- sd_simulate(ds_inputs, start_time = 0, stop_time = 1000, 
                      timestep = 1 / 64,
                      integ_method = "euler") |> 
  mutate(c     = C / pop_val,
         R_aux = estimate_R0_ti(var_theta, beta_vals[[2]], iota_mid, bio_params),
         Rt = (S / pop_val) * R_aux)
```

```{r}
no_df <- base_df |> filter(R0 == 3) |> 
  rename(c = c_base) |> 
  select(time, c, Rt) |> 
  mutate(var_theta = 0,
         model = "no intervention")
```


```{r, fig.height = 3.5, fig.width = 3, warning = FALSE}
ti_df <- output |> select(time, c, var_theta, Rt) |> 
  mutate(model = "T&I")

ti_ref2 <- output |> select(time, C_in) |> 
  mutate(model = "T&I",
         `Contact tracing rate` = 0)


df <- bind_rows(no_df, ti_df) |> 
  rename(`theta[t]`  = var_theta,
         "\u211c[t]" = Rt) |> 
  pivot_longer(c(-time, - model))
```

```{r}
set.seed(600)

sobol_design(lower = c(par_rho_d = 0,
                       par_alpha_d = alpha_d_val),
             upper = c(par_rho_d   = rho_est * 10,
                       par_alpha_d = alpha_d_val * 10),
             nseq = 5000) -> pars_df

pars_df <- pars_df |> bind_rows(data.frame(par_rho_d   = rho_est,
                                           par_alpha_d = alpha_d_val))

consts_df <- pars_df
```

```{r}
plot(pars_df)
```

```{r}
iota_vals  <- c(0.43, 0.51, 0.62) 

comb_df           <- expand_grid(delta_vals, iota_vals)
colnames(comb_df) <- c("dv", "iv")

map_df(transpose(comb_df), \(comb_obj) {
  
  dv <- comb_obj$dv
  iv <- comb_obj$iv
  
  consts_df$par_delta  <- dv
  consts_df$par_iota_d <- iv

  fn <- str_glue("./saved_objects/model_03_delta_{dv}_iota_{iv}.rds")
  
  if(!file.exists(fn)) {
    
    tic()
    sens <- sd_sensitivity_run(ds_inputs, consts_df, 
                               start_time = str_time, 
                               stop_time = stp_time, 
                               timestep = 1 / 64,
                               integ_method = "euler", multicore = TRUE,
                               reporting_interval = 1/8) 
   
    
    df <- sens |> 
      select(time, S, iter, par_beta, C, par_alpha_d, par_rho_d,
                         par_delta, var_theta, par_iota_d)
    
    R_aux <- estimate_R0_ti(df$var_theta, beta_vals[[2]], df$par_iota_d, 
                            bio_params)
    
    df <- df |>
      mutate(c  = C / pop_val,
             Rt = (S / pop_val) * R_aux)
    
    output <- df |> 
      mutate(diff_rt = 1 - Rt) |> 
      filter(diff_rt > 0) |> 
      group_by(iter, par_delta, par_iota_d) |> 
      filter(diff_rt == min(diff_rt)) |> ungroup() |> 
      select(par_delta, iter, time, par_rho_d, par_alpha_d, par_iota_d) |> 
      mutate(time_star = time - ref_time)
    
    saveRDS(output, fn)
    
    toc()
  
  } else output <- readRDS(fn)
  
  output
}) -> time_thres_df
```

```{r}
fp <- "./models/03b_Testing_Isolation.stmx"

mdlb       <- read_xmile(fp, stock_list = list(Qd = data_df[1, 2]),
                        const_list = c(bio_params,
                                       par_beta   = beta_vals[[2]],
                                       par_iota_d  = iota_mid))
```

```{r}
map_df(delta_vals, \(delta_val) {
  
  consts_df$par_delta  <- delta_val
  
  fn <- str_glue("./saved_objects/model_03b_delta_{delta_val}.rds")
  
  if(!file.exists(fn)) {
  
    tic()

    sens <- sd_sensitivity_run(mdlb$deSolve_components, consts_df, 
                               start_time = str_time, 
                               stop_time = stp_time, 
                               timestep = 1 / 64,
                               integ_method = "euler", multicore = TRUE,
                               reporting_interval = 1/8) 
    
    
    df <- sens |> 
      select(time, S, iter, par_beta, C, par_alpha_d, par_rho_d,
                         par_delta, var_theta, par_iota_d)
    
    R_aux <- estimate_R0_ti(df$var_theta, beta_vals[[2]], df$par_iota_d, 
                            bio_params)
    
    df <- df |>
      mutate(c  = C / pop_val,
             Rt = (S / pop_val) * R_aux)
    
    output <- df |> 
      mutate(diff_rt = 1 - Rt) |> 
      filter(diff_rt > 0) |> 
      group_by(iter, par_delta, par_iota_d) |> 
      filter(diff_rt == min(diff_rt)) |> ungroup() |> 
      select(par_delta, iter, time, par_rho_d, par_alpha_d, par_iota_d) |> 
      mutate(time_star = time - ref_time)
    
    saveRDS(output, fn)
    toc()
  
  } else output <- readRDS(fn)
  
  output
}) -> time_thres_df2
```



```{r, warning = FALSE, fig.height = 7, fig.width = 7}
g <- plot_fig_06(df, time_thres_df, time_thres_df2)

ggsave("./plots/Fig_06_Testing_analysis.pdf", plot = g, 
       height = 7, width = 7, device = cairo_pdf)

g
```

# Contact tracing

## $\Re_0$ analytical expression

### F matrix

```{r, message = FALSE}
F_matrix           <- read_csv("./Data/CT_F_matrix.csv", show_col_types = FALSE)
c_names            <- colnames(F_matrix)
c_names[1]         <- ""
colnames(F_matrix) <- c_names

F_matrix |>
  kbl(escape = FALSE) |> kable_styling(full_width = FALSE)
```

### V matrix

```{r, message = FALSE}
F_matrix           <- read_csv("./Data/CT_V_matrix.csv", show_col_types = FALSE)
c_names            <- colnames(F_matrix)
c_names[1]         <- ""
colnames(F_matrix) <- c_names

F_matrix |>
  kbl(escape = FALSE) |> kable_styling(full_width = FALSE)
```

### Spectral radius (largest eigenvalue)

\begin{equation}

a = \sqrt{\gamma ^4 \kappa ^2 \upsilon ^2 \left((\gamma  (\zeta  \eta  \nu  (\omega -1)-\zeta  \kappa  \omega + \zeta^k \theta  \kappa  \omega )+\zeta  \kappa  \nu  \omega  (\theta  \iota^d -1))^2-4 \gamma  \zeta  \zeta^k \theta  (\iota^d -1) \kappa  \omega  (\gamma  \eta  (\nu -\nu  \omega )+\gamma  \kappa  \omega +\kappa  \nu  \omega )\right)}

\end{equation}

\begin{equation}

b = \gamma ^3 \kappa  \upsilon  (\zeta  \eta  (\nu -\nu  \omega )+\zeta  \kappa  \omega - \zeta^k \theta  \kappa  \omega )+\gamma ^2 \zeta  \kappa ^2 \nu  \upsilon  \omega  (1-\theta  \iota^d )

\end{equation}

\begin{equation}

\Re_0 = \frac{a + b}{2 \gamma ^3 \kappa ^2 \nu}

\end{equation}

## Partial calibration

```{r}
data_FTE <- data.frame(time  = c(0, 60, 90, 210),
                      value = c(200, 670, 1250, 3250)) 

est_obj     <- estimate_rho(data_FTE)
rho_k_est   <- est_obj$estimate
```


```{r}
ggplot(est_obj$sim, aes(time, Q)) +
  geom_line() +
  geom_point(data = data_FTE, aes(y = value), colour = "red") +
  theme_classic()
```

```{r}
fp_ct <- "./models/04_Contact_tracing.stmx"

zeta_val   <- beta_vals[[2]] * 10

# Number of index cases traced per week
idx_val <- 3

Qk_init     <- (data_FTE[1, 2] * idx_val * zeta_val / 7) * (1000 / pop_val)
alpha_k_val <- (data_FTE[4, 2] * idx_val * zeta_val / 7) * (1000 / pop_val)

iota_mid <- 0.51

alpha_d_val <- data_df[4, 2]

mdl       <- read_xmile(fp_ct, stock_list = list(Qd = data_df[1, 2],
                                              Qk = Qk_init),
                        const_list = c(bio_params,
                                       par_zeta    = zeta_val,
                                       par_alpha_d = alpha_d_val,
                                       par_alpha_k = alpha_k_val,
                                       par_rho_d   = rho_est,
                                       par_rho_k   = rho_k_est,
                                       par_iota_d  = 0.51,
                                       par_delta   = 0.60))
ds_inputs <- mdl$deSolve_components
```

```{r}
sim_output <- sd_simulate(ds_inputs, start_time = 0, stop_time = 300, timestep = 1/32,
            integ_method = "euler")
```


```{r}
ct_df <- sim_output |> select(time, C_in, k, Dk) |> 
  mutate(`Contact tracing rate` = k/Dk,
         model = "CT") |> 
  select(-k, -Dk)
  

comparison_ti_ct <- bind_rows(ct_df, ti_ref2) |> 
  filter(time >= 1) |> 
  mutate(C_in = C_in / pop_val) |> 
  rename(`Incidence rate` = C_in) |> 
  pivot_longer(c(-time, -model))
```

```{r}
set.seed(19860618)

sobol_design(lower = c(par_rho_k = 0,
                       par_alpha_k = alpha_k_val),
             upper = c(par_rho_k   = rho_k_est * 10,
                       par_alpha_k = alpha_k_val * 10),
             nseq = 5000) -> pars_df

pars_df <- pars_df |> bind_rows(data.frame(par_rho_k   = rho_k_est,
                                           par_alpha_k = alpha_k_val))

consts_df <- pars_df
```

```{r}
plot(pars_df)
```


```{r}
scenarios_df <- data.frame(Testing_Scenario = rep(1:3, 2),
                           Qd       = rep(c(data_df[1, 2],
                                            alpha_d_val,
                                   10 * alpha_d_val), 2),
                  alpha_d  = rep(c(alpha_d_val,
                                   alpha_d_val,
                                   10 * alpha_d_val), 2),
                  iota = c(rep(iota_vals[[2]], 3),
                           rep(iota_vals[[3]], 3)))

scenarios_list <-  scenarios_df |> transpose()
```

```{r}
# Testing capacity
test_cap <- map_df(scenarios_list[1:3], \(sce_obj) {
  
    mdl <- read_xmile(fp_ct,
                    stock_list = list(Qd = sce_obj$Qd,
                                      Qk = Qk_init),
                    const_list = c(bio_params,
                                   par_zeta    = zeta_val,
                                   par_alpha_d = sce_obj$alpha_d,
                                   par_alpha_k = alpha_k_val,
                                   par_rho_d   = rho_est,
                                   par_rho_k   = rho_k_est,
                                   par_iota_d  = iota_mid,
                                   par_delta   = 0.60))
    
    sim_out <- sd_simulate(mdl$deSolve_components, start_time = 0,
                         stop_time = 300, timestep = 1/64,
                         integ_method = "euler") |>
      filter(time - trunc(time) == 0) |> 
      select(time, Qd) |> mutate(Scenario = sce_obj$Testing_Scenario)
})
```

```{r}
results_df <- map_df(scenarios_list, \(sce_obj) {
  
  iv  <- sce_obj$iota
  tsc <- sce_obj$Testing_Scenario

  mdl <- read_xmile(fp_ct,
                    stock_list = list(Qd = sce_obj$Qd,
                                      Qk = Qk_init),
                    const_list = c(bio_params,
                                   par_zeta    = zeta_val,
                                   par_alpha_d = sce_obj$alpha_d,
                                   par_alpha_k = alpha_k_val,
                                   par_rho_d   = rho_est,
                                   par_rho_k   = rho_k_est,
                                   par_iota_d  = iv,
                                   par_delta   = 0.60))
  
  fn <- str_glue("./saved_objects/model_04_{tsc}_iota_{iv}.rds")

  if(!file.exists(fn)) {

    tic()

    sens <- sd_sensitivity_run(mdl$deSolve_components,
                               consts_df          = consts_df,
                               start_time         = 0,
                               stop_time          = 300,
                               timestep           = 1 / 64,
                               integ_method       = "euler",
                               multicore          = TRUE,
                               reporting_interval = 1/8)

    df <- sens |>
      select(time, S, iter, par_zeta, par_upsilon, C, var_theta, par_iota_d,
             par_alpha_k, par_rho_k, var_zeta_k, C_in)
    
    peak_df <- df |> group_by(iter) |> 
      filter(C_in == max(C_in)) |> ungroup() |> 
      select(iter, C_in) |> 
      rename(c_dot_max = C_in)

    R_aux <- estimate_R0_ct(df$par_zeta, 0.1, df$var_theta, df$par_iota_d,
                            df$var_zeta_k, bio_params)

    df <- df |>
      mutate(c        = C / pop_val,
             Rt       = (S / pop_val) * R_aux,
             test_sce = sce_obj$Testing_Scenario)

    output <- df |>
      mutate(diff_rt = 1 - Rt) |>
      filter(diff_rt > 0) |>
      group_by(iter, test_sce, par_iota_d) |>
      filter(diff_rt == min(diff_rt)) |> ungroup() |>
      select(iter, time, par_rho_k, par_alpha_k, test_sce, var_zeta_k,
             par_zeta, par_iota_d) |>
      mutate(time_star = time - ref_time) |> 
      left_join(peak_df, by = "iter")

    saveRDS(output, fn)

    toc()

  } else output <- readRDS(fn)

  output
})
```

```{r}
cap_sce <- scenarios_df[2:3, ] |> 
  mutate(par_alpha_k = alpha_k_val * 100,
         par_rho_k   = rho_k_est * 10) |> 
  rename(par_alpha_d = alpha_d)

mdl <- read_xmile(fp_ct,
                  stock_list = list(Qk = Qk_init),
                    const_list = c(bio_params,
                                   par_zeta    = zeta_val,
                                   par_rho_d   = 0,
                                   par_iota_d  = unique(cap_sce$iota),
                                   par_delta   = 0.60))

c_df <- cap_sce |> select(-Testing_Scenario, -Qd, -iota)
s_df <- cap_sce |> select(Qd)

sens <- sd_sensitivity_run(mdl$deSolve_components,
                           consts_df = c_df,
                           stocks_df = s_df,
                           start_time         = 0,
                           stop_time          = 300,
                           timestep           = 1 / 64,
                           integ_method       = "euler",
                           multicore          = TRUE,
                           reporting_interval = 1/8) |> 
  filter(time > 0)
```

```{r}
grid_df <- expand.grid(var_theta = seq(0, 1, 0.001), zeta_star = seq(0, 1, 0.001))

R0_sens <- map_df(c(0.5, 0.75, 1), \(iota_val, grid_df) {
  
  R0_est <- estimate_R0_ct(beta_vals[[2]] * 10, par_upsilon = 0.1,
                           var_theta =  grid_df$var_theta, 
                           par_iota  = iota_val, 
                           var_zeta_k = beta_vals[[2]] * 10 * grid_df$zeta_star,
                           bio_params)
  
  grid_df$R0 <- R0_est
  
  grid_df |> mutate(par_iota_d = iota_val)
}, grid_df = grid_df)
```



```{r}
ggplot(R0_sens, aes(var_theta, zeta_star, r0)) +
  facet_wrap(~par_iota_d) +
  geom_raster(aes(fill = R0)) +
  scale_fill_viridis_b(breaks = c(1, 1.5, 2, 2.5, 3),
                       option = "C", direction = -1) +
  theme_classic()
```

```{r, warning = FALSE, fig.height = 7, fig.width = 7}
g <- plot_fig_08(comparison_ti_ct, test_cap, results_df)

ggsave("./plots/Fig_08_CT_analysis.pdf", plot = g, 
       height = 7, width = 7, device = cairo_pdf)

g
```



